Hedonic Analysis over Time and Space:\\ The Case of House Prices and Traffic Noise

### 2014-08-18 reports/NoiseHedonicRaR.Rnw
contains the final version of NoiseHedonicRaR that was (re)submitted to JoRS

\title{Traffic Noise and House Prices: A Hedonic Analysis over Time and Space}
\date{}
\author{}%Aaron Swoboda, Tsegaye Nega and Maxwell Timm}

\doublespacing
\begin{document}
\maketitle
\pagenumbering{roman}
\begin{singlespace}
\begin{abstract}
One consequence of the expanding road network and its associated traffic is increased levels of traffic noise.  While the hedonic literature has consistently found a negative effect of this phenomenon on the real estate market, research in the United States has often relied on crude measures of traffic noise. Here, we reduce the measurement error of traffic noise exposure through a detailed model of noise propagation over the landscape. We then estimate the hedonic relationship between noise and house prices using over 40,000 single family home transactions throughout the St.\ Paul, Minnesota, urban area from 2005-2010. We implement spatially and temporally flexible local regression techniques and find significant non-stationarity in the hedonic function over time and space.
\end{abstract}
\end{singlespace}

@@

% Automobiles are already perhaps the greatest source of noise in residential neighborhoods \citep{Barber2010} and traffic noise was estimated to cause around three billion dollars worth of external damage to the United States economy alone in 1991 \citep{Delucchi1998}. Traffic noise and its attendant problems are greater now than they were in the 1990s and predicted to worsen in the future \citep{Goines2007}.  %With the exception of a slight dip during the economic recession in the late 2000s, the number of vehicle miles traveled in the United States has steadily increased for the past 50 years.\footnote{\url{http://www.fhwa.dot.gov/policyinformation/statistics/2011/pdf/rc1c.pdf}} 
% Globally, \citet{Dargay2007} predict the number of personal vehicles to grow from roughly 800 million in 2002 to over two billion units by 2030. Additionally, the global trend of increased urbanization is expected to continue, with the proportion of the population living in cities growing from roughly half now to over two-thirds by the middle of the century \citepalias{UNDESA2012}.

One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels. \citet{Nelson1982} reviewed nine of the earliest noise hedonic articles in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel. Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities). Recent hedonic research has tended to focus on the European experience, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.

%Reviews of the research by \citet{Bateman2001} found that the negative effect of traffic noise on house prices ranged from 0.08 to 2.22 percent per decibel with a mean around 0.55 percent per decibel, while \citet{Navrud2002} found an average decrease of 0.64 percent per decibel. Much of the

@@

In this paper, we estimate a hedonic relationship between traffic noise and single family house prices across 44 cities and several hundred square miles in the St.\ Paul, Minnesota, urban region by taking advantage of a uniquely detailed set of noise estimates. The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and land cover on noise propagation. More detail about the noise model inputs and procedures are presented in the next section of the paper.

In addition to using new data that reduces the measurement error of traffic noise, we construct a flexible hedonic model that allows for non-stationary relationships between house prices and our explanatory variables over geography and time. Such Locally Weighted Regression (LWR) models have become increasingly prevalent in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, McMillen2010, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other standard spatial econometric models under common real world circumstances \citep{McMillen2012}. Our results confirm the importance of a spatially- and temporally-flexible modeling approach and reject the still too often used assumptions of spatial and temporal stationarity in the hedonic function.

@@

\subsection{Time}
We collected sales transactions from 2005 to 2010 to estimate the hedonic price function over time and test for differences before, during, and after the economic recession. We are concerned about issues of sample selection bias over time, however we find no evidence of only certain types or locations of houses transacting in later years compared to earlier years in our data. Table \ref{tab:SumStatsTime} displays the mean variable values by year of sale to look for differences over time. The mean sale price in 2009 (roughly \$230,000) was almost 20 percent lower than the mean sale price in 2006 (roughly \$280,000). However, most other variable means have small or no differences in the across time.\footnote{We also created univariate density plots of the variables by year to check for differences in the shape and spread of the distributions over time. With the exception of house prices, we found no differences in the variable distributions over time. Figures available upon request.} We also mapped the locations of sales transactions to check for differences in geographic dispersion of sales over time, but found none (see Figure~\ref{fig:SalesYear}). Thus, with the exception of lower sales prices in later years, house characteristics in our sample appear similar before, during, and after the economics recession.

@@

% \begin{figure}
% \makebox[\textwidth][c]{\includegraphics[height = \textheight]{../graphs/DensityPlotsByYear}}
% \caption{This figure shows the distribution of our variables over time. Note that there are no discernable differences in mean, standard deviation, or shape of the distribution for most variables other than sales price.}
% \label{fig:DensityPlots}
% \end{figure}

@@

\section{Basic Econometric Model}\label{basicModel}
Consistent with past research, this study estimates a semi-logarithmic hedonic price functon.  Before implementing the Locally Weighted Regression model, we present the results of a simpler econometric model given by equation~\eqref{eq:model}.
\begin{equation}\label{eq:model}	
ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
\end{equation}
Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects. Model (A) in Table \ref{tab:globalRegression} displays the results of this basic Ordinary Least Squares regression model. In addition to the important structural and neighborhood variables, we also include fixed effects for each city and an interaction term between month and year of sale in the dataset to allow for unique month-to-month price shocks. The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.

@@

\section{Locally Weighted Regression Model}
Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Cleveland1988}, \citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others. It is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
\begin{equation}\label{eq:LWRbeta}
\hat{\beta}_i = (X'W_iX)^{-1}X'W_iY,
\end{equation}
where X is a $n \times m$ matrix of independent variables, $W_i$ is the $n \times n$ weights matrix, and Y is the $n \times 1$ vector of dependent variable values. The weights matrix, $W_i$ is a diagonal matrix where element $w_{jj}$ denotes the weight that the $j^{th}$ data point will receive in the regression coefficients estimated at location $i$ in the dataset. We employ a bi-square weights function and a k-nearest neighbor bandwidth approach as described in equation~\eqref{eq:weights}, 
\begin{equation}\label{eq:weights}
w_{jj}=\left[1-\left(\frac{d_{ij}}{d_{k}}\right)^2 \right]^2 \textrm{ if  }d_{ij}<d_{ik}\textrm{, otherwise = 0},
\end{equation}
where $d_{ij}$ denotes the distance between observations $i$ and $j$, and $d_{ik}$ is the distance from observation $i$ to the $k^{th}$ nearest observation. This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation. We estimate LWR coefficients using bandwidths ranging from as small as $k=100$ observations and as large as 4,000 observations.

@@

%\section{Results}
Similar to the basic econometric model described in Section \ref{basicModel}, we estimated the LWR model with logged sales price as a function of structural and neighborhood variables, location and time. In order to account for changing market conditions over time, when estimating the LWR model for a particular observation in our data, we used only houses sold within the past 12 months and also included month fixed effects to account for seasonality and other changes such as tax credits for home purchases. Thus, the coefficient estimates at a particular house were estimated using data from other sales nearby in both time and geography.

@@

\begin{figure}
  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModel}}
\caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models. For comparison, the GCV scores for each model when estimated at a global scale are also shown. Note that the LWR models all have significantly smaller GCV scores than the global models. The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 500 nearest houses.}\label{fig:GCVmodel}
\end{figure}

@@

The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant) and also more negative than the OLS value presented previously. Unsurprisingly, the dispersion of the coefficient distributions are greater for the smaller bandwidths. We now turn to investigating whether this increased spread is due to the stochastic nature of smaller sample sizes or spatial heterogeneity in the hedonic function. In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy due to significant spatial and temporal variation in the hedonic function.

@@

We first conducted a Monte Carlo simulation recommended by \citet{Fotheringham2002}. We repeatedly resampled (without replacement) the locations of our house transactions and calculated the GCV scores for multiple different LWR model bandwidths. By comparing the actual GCV scores from our data to those with the simulated data we can test the hypothesis that our improved model fit was due to random chance. The intuition of the test is as follows - if we observe similar improvements in model fit with different spatial arrangements of our data, we conclude that the improved model fit in our actual data could have been due to random chance. Failing to recreate a spatial arrangement that yields a similar model fit as to that obtained with our actual data is then evidence that our spatial arrangement and the improved model fit obtained from a spatially heterogeneous model is unique.

We conducted 100 different experiments using 10 different bandwidths ranging from the nearest 100 to 4,000 sales (within the past 12 months). After running a thousand different local regression models with the simulated data, we never obtained model performance anywhere near our actual model fit at a bandwidth of 500 nearest sales. Second, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size: in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth. This is in stark contrast to our results with the actual data which had a significant reduction in GCV score for local analysis.

@@

The previous section presented evidence in support of the claim that there exists significant spatial variation in the hedonic function. However, we have not yet established which variables have spatially varying coefficients. Figures~\ref{fig:AcreBetas}--\ref{fig:NoiseBetas} show the spatial variation in the estimated LWR coefficients for three important variables, lot size, house size, and noise. For comparison, we present the results across four different levels of local analysis, ranging from LWR bandwidths of 500 nearest houses to the nearest 2,000 sales.

A few patterns are clear. Figure~\ref{fig:AcreBetas} shows that the hedonic coefficient on lot size is largest near the central business district of St.\ Paul. Consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD. This tendency is consistent across the four different bandwidths, whenever our model ``allowed'' the lot size coefficient to vary over space we saw patterns like these.\footnote{Results for other bandwidths available upon request.}

The LWR coefficients on house size (measured in thousands of square feet of finished space) also seem to exhibit spatial variation in Figure~\ref{fig:HouseBetas}. In the west-central portion of our study area (a collection of notably desirable neighborhoods nestled between the Minneapolis and St.\ Paul CBDs) we see a cluster of large LWR coefficients, while those areas in the southernmost portion of our region (suburban areas) have the smallest coefficients.

@@

We conducted a second series of simulation experiments aimed at testing whether the spatial variation exhibited in particular coefficients was significant or due to random chance. The mechanics of the second simulation are very similar to the those described in the previous section. We randomly changed the spatial arrangement of our house sales and re-estimated the LWR model. However, in this simulation we compared the \emph{spread} of the regression coefficients (as measured by the standard deviation).\footnote{Whereas in the first simulation we compared the model fit.} If we observed similar levels of dispersion for variable coefficients in the randomly arranged data as in our true data, then we cannot reject the null hypothesis of a stationary relationship. However, significantly \emph{greater} dispersion of regression coefficients with our actual data would provide evidence consistent with the variable having a non-stationary relationship.

We conducted this experiment 100 times and obtained similar results for several different bandwidths. For most variables, the standard deviation of the LWR coefficients obtained with our actual data was significantly greater than any standard deviation obtained with the randomized simulated data. We never observed a level of coefficient dispersion anywhere near the actual coefficient standard deviations for variables like house size, lot size, and most others. This can be seen in Figure~\ref{fig:MCsim2} by comparing the dashed lines of a given color to the respective solid colored distributions.\footnote{For brevity's sake we present the results for the 500 and 2,000 bandwidth sizes in Figure~\ref{fig:MCsim2}. Additional results available on request.} However, for variables like noise, owner occupancy and percent of the census block population under age 18, our observed spread in the actual LWR coefficients is similar to the simulated data. In these cases we therefore do not reject the null hypothesis of spatial stationarity. Overall, this simulation suggests that most of our variables seem to exhibit a significant non-stationary relationship with logged sales prices, but noise does not seem to be one of them.

\begin{figure}
 \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsimResultsSDsk500and2000final}}
 \caption{This figure shows the actual standard deviation in LWR coefficients (dashed line) compared to standard deviations obtained from 100 different instances of spatial randomization (solid lines). Results are presented for two different bandwidths (nearest 500 and 2,000 denoted by color) for each explanatory variable. In all cases the distribution of standard deviations for the smaller bandwidth is larger. In most cases the standard deviation of LWR coefficients for the actual data is substantially higher than any standard deviation obtained with the simulated data, but not for the noise variable.}
 \label{fig:MCsim2}
\end{figure}

@@

House prices fell dramatically in the United States during and after the Great Recession of 2008-09. We know little about the patterns of change in the hedonic price functions during and after the fall in house prices. Figures~\ref{fig:AcreTime}--\ref{fig:NoiseTime} show the spatial distribution of some our LWR hedonic coefficients for bandwidths of 500 and 2,000 nearest sales for the years 2006--2010.  The estimated LWR coefficients are different over time. In particular, the positive lot size and house size coefficients tend to decrease over time. These results are consistent with standard economic theory, as wealth and income decrease, consumer willingness to pay for normal goods decreases. What is surprising, however, is that the negative noise coefficient estimates also tend to be more negative in later years of our study. Figure~\ref{fig:NoiseTime} shows that the spatial patterns are similar across years (the most negative coefficients tend to be in the same locations across years), but the average noise coefficient tends to be more negative for the later years.

@@

Our noise variable is also a model estimate, not a direct measurement of the noise levels encountered by house purchasers. The model controls for the most important determinants of average noise exposure-- the level of the noise source, the distance and elevation change from the source, the intervening buildings, sound barriers, and foliage, but of course there is undoubtedly error. House purchasers may have visited the property on particularly busy traffic days, or on days with weather conditions more or less conducive to noise propagation across the landscape. Future researchers may seek to collect actual noise exposure data, but this will be a daunting task.

Our work faces other notable data limitations. While our house sales data were collected over the course of six years, the noise estimates are for the year 2007. To the extent that traffic flows changed with the economic recession, our noise variable could be inaccurate for other years. However, we believe these potential changes are miniscule. Table~VM2 from the US. Department of Transportation Office of Highway Policy Information website reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0 million vehicle miles. Overall, this represents a change of less than 10 percent. \footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} Such small changes in total vehicle miles traveled will not yield significant differences in noise level estimates from our model. Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper, but may be a worthwhile investment for future work seeking to test the robustness of our results.

@@

Monte Carlo simulation results suggest that the better goodness-of-fit provided by the local models were not due to chance and that many hedonic implicit prices vary over space within our study area. When the location of our data was randomly assigned and our LWR model was re-estimated across multiple different bandwidths, in 100 consecutive simulations the smallest GCV score was obtained when the data were analyzed at a pooled/global level rather than local. That is, after trying thousands of different combinations of varying levels of local analysis with the spatially redistributed data, local analysis never fit the randomized data better than global analysis and we never came close to estimating our observed house sales prices as well as we did with the local analysis on the actual data.

Additionally, re-estimating the LWR model using local bandwidths but randomly assigned locations yielded substantially smaller standard deviations for the majority of our regression coefficients. Such differences suggest that the variation exhibited by most of our regression coefficients was indeed spatial non-stationarity and not due to random chance. While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of a few variables to have  a standard deviation in the spatially randomized data similar to that obtained with the actual data.

@@

Future research should be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited. Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are allowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression. Future work may also seek to re-estimate traffic noise models over time to better account for changes in traffic flows associated with macroeconomic conditions. Lastly, researchers should take advantage of the recent suggestions in \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics.

>>>>

\title{Hedonic Analysis over Time and Space:\\ The Case of House Prices and Traffic Noise}
\date{}
\author{}%Aaron Swoboda, Tsegaye Nega and Maxwell Timm}

\doublespacing
\begin{document}
\maketitle
\pagenumbering{roman}
\begin{singlespace}
\begin{abstract}
One consequence of the expanding road network and its associated traffic is increased levels of traffic noise.  While the hedonic literature has consistently found a negative relationship between real estate prices and noise levels, research in the United States has typically relied on crude measures of traffic noise. Here, we reduce the measurement error of traffic noise exposure through a detailed model of noise propagation over the landscape. We then estimate the hedonic relationship between noise and single family house prices using over 40,000 transactions throughout the St.\ Paul, Minnesota, urban area from 2005-2010. We implement spatially and temporally flexible local regression techniques and find significant non-stationarity in the hedonic function over time and space.
\end{abstract}
\end{singlespace}

@@

Hedonic analysis is one way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) by examining the relationship between house prices and noise levels. \citet{Nelson1982} reviewed nine of the earliest hedonic studies in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel. Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities). Recent hedonic research has tended to focus on the European experience, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.

@@

In this paper, we take advantage of a uniquely detailed set of noise data to estimate the hedonic price function for over 40,000 single family house transactions across several hundred square miles in the St.\ Paul, Minnesota, urban region from 2005-2010.  The data represent perhaps the most accurate regional noise estimates ever used in the hedonic literature in the United States to date due to the high spatial resolution of the estimates (10 m x 10 m) and the incorporation of the effects of nearby buildings and land cover on noise propagation. More detail about the noise model inputs and procedures are presented in the next section of the paper.

In addition to using new data that reduces the measurement error of traffic noise, we construct a flexible hedonic model that allows for non-stationary relationships between house prices and our explanatory variables over geography and time. Such Locally Weighted Regression (LWR) models have become increasingly prevalent in published work \citep[see][]{MarmolejoDuarteCarlos;GonzalezTamez2009, McMillen2010, Carruthers2010, Sunding2010, Nappi-Choulet2011} and have been shown to be more accurate than other standard spatial econometric models under common real world circumstances \citep{McMillen2012}. Our results confirm the importance of a spatially- and temporally-flexible hedonic modeling approach and reject the still too often used assumptions of spatial and temporal stationarity in the regression function.

@@

\subsection{Time}
Due to concerns of sample selection bias before, during, and after the economic recession, we compared the characteristics of our data by year to look for important differences. Table \ref{tab:SumStatsTime} displays the mean variable values by year of sale. The mean sale price in 2009 (roughly \$230,000) was almost 20 percent lower than the mean sale price in 2006 (roughly \$280,000). However, most other variable means show small or no differences across years.\footnote{We also created univariate density plots of the variables by year to check for differences in the shape and spread of the distributions over time. With the exception of house prices, we found no differences in the variable distributions over time. Figures available upon request.} We also mapped the locations of sales transactions to check for differences in geographic dispersion of sales over time, but found none (see Figure~\ref{fig:SalesYear}). Thus, with the exception of lower sales prices in later years, house characteristics in our sample appear similar before, during, and after the economic recession. Of course, it is still possible that the houses differed over time in unobserved characteristics.

@@

@@

\section{Basic Econometric Model}\label{basicModel}
Consistent with past research, this study estimates a semi-logarithmic hedonic price functon.  Before implementing the Locally Weighted Regression model, we present the results of a simpler econometric model given by equation~\eqref{eq:model}.
\begin{equation}\label{eq:model}	
ln \textrm{ Sale Price}_i = \beta _0 + \beta _1 \textrm{Noise}_i+ \beta _2 S_i+ \beta _3 N_i + \beta _4 T_i + \textrm{error}_i
\end{equation}
Noise$_i$ is the noise level for house $i$, $S_i$ is a vector of the house's structural attributes, $N_i$ is a vector of the neighborhood attributes, and $T_i$ is a vector of time fixed effects. Model (A) in Table \ref{tab:globalRegression} displays the results of this basic Ordinary Least Squares regression model. In addition to the important structural and neighborhood variables, we also included fixed effects for each city and an interaction term between month and year of sale. The traffic noise coefficient suggests houses in our data that are similar in all respects but a one decibel difference in noise will, on average, have sales prices roughly 0.27 percent lower at the noisier location.

@@

\section{Locally Weighted Regression Model}
Locally Weighted Regression (LWR) techniques (also known as Geographically Weighted Regression) are described in detail by \citet{Cleveland1988}, \citet{Brunsdon1998b}, \citet{Fotheringham2002}, and others. LWR is a weighted least squares methodology in which regression coefficients are estimated over space as a function of the local data as described in Equation~\eqref{eq:LWRbeta},
\begin{equation}\label{eq:LWRbeta}
\hat{\beta}_i = (X'W_iX)^{-1}X'W_iY,
\end{equation}
where X is a $n \times m$ matrix of independent variables, $W_i$ is the $n \times n$ weights matrix, and Y is the $n \times 1$ vector of dependent variable values. The weights matrix, $W_i$ is a diagonal matrix where element $w_{jj}$ denotes the weight that the $j^{th}$ data point will receive in the regression coefficients estimated at location $i$ in the dataset. We employ a bi-square weights function and a k-nearest neighbor bandwidth approach as described in equation~\eqref{eq:weights}, 
\begin{equation}\label{eq:weights}
w_{jj}=\left[1-\left(\frac{d_{ij}}{d_{k}}\right)^2 \right]^2 \textrm{ if  }d_{ij}<d_{ik}\textrm{, otherwise = 0},
\end{equation}
where $d_{ij}$ denotes the distance between observations $i$ and $j$, and $d_{ik}$ is the distance from observation $i$ to the $k^{th}$ nearest observation. This function assigns weights close to 1 for data points near observation $i$, weights positive but closer to zero for observations farther away, and zero for all $n-k$ observations farther away than the $k^{th}$ nearest observation. We estimate LWR coefficients using bandwidths ranging from as small as $k=100$ observations and as large as 4,000 observations.

@@

%\section{Results}
Similar to the basic econometric model described in Section \ref{basicModel}, we estimated the LWR model with logged sales price as a function of structural and neighborhood variables, location and time. In order to account for changing market conditions over time, when estimating the LWR model for a particular observation in our data, we used only houses sold within the past 12 months and also included month fixed effects to account for seasonality and other policy changes such as tax credits for home purchases. Thus, the coefficient estimates at a particular house were estimated using data from other sales nearby in both time and geography.

@@

\begin{figure}
  \makebox[\textwidth][c]{\includegraphics[width = 1.2\textwidth]{../graphs/GCVbyModelFinal}}
\caption{This figure shows the relationship between bandwidth size and the GCV score for three different Locally Weighted Regression (LWR) models. For comparison, the GCV scores for each model when estimated at a global scale are also shown. Note that the LWR models all have significantly smaller GCV scores than the global models. The minimum GCV score is obtained by LWR Model (3) at a bandwidth of 500 nearest houses.}
\label{fig:GCVmodel}
\end{figure}

@@

The mean LWR coefficient for the noise variable is similar across the different bandwidths (approximately a third of a percent difference in house sales prices for each additional decibel of noise, all other varibles held constant) and also more negative than the OLS value presented previously. In the next three subsections we describe the results of hypothesis tests that lead us to believe that LWR modeling is an appropriate and beneficial research strategy due to significant spatial and temporal variation in the hedonic function.

@@

We first conducted a Monte Carlo simulation recommended by \citet{Fotheringham2002}. We repeatedly resampled (without replacement) the locations of our house transactions and calculated the GCV scores for LWR models across multiple bandwidths. We then compared the GCV scores obtained with our actual data to those from the simulated data to see if other spatial arrangements of the data could yield similar model fit.

We conducted 100 different experiments in which we estimated LWR models across 10 different bandwidths each time. In a thousand different local regression models with the simulated data, we never obtained model performance anywhere near our actual model fit at a bandwidth of 500 nearest sales. Second, in constrast to the clear positive relationship between bandwidth size and GCV score in Figure~\ref{fig:GCVmodel}, the simulated data consistently produced an inverse relationship between GCV scores and bandwidth size (in every single experimental iteration the smallest GCV score was obtained at the largest bandwidth).

@@

The previous section presented evidence in support of the claim that there exists significant spatial variation in the hedonic function. However, we have not yet established which variables have spatially varying coefficients. Figures~\ref{fig:AcreBetas}--\ref{fig:NoiseBetas} show the spatial variation in the estimated LWR coefficients for three important variables, lot size, house size, and noise. For comparison, we present the results across four different LWR bandwidths ranging from 500 to 2,000 nearest sales.

A few patterns are clear. Figure~\ref{fig:AcreBetas} shows that the hedonic coefficient on lot size is largest near the central business district of St.\ Paul. Consistent with standard urban economic theory, to the extent that the hedonic coefficient is correlated with the price of land, our results suggest the price of land is highest near the central business district and declines with distance from the CBD. This tendency is consistent across the different bandwidths, whenever our model ``allowed'' the lot size coefficient to vary over space we saw patterns like these.\footnote{Results for other bandwidths available upon request.}

The LWR coefficients on house size also seem to exhibit spatial variation in Figure~\ref{fig:HouseBetas}. In the west-central portion of our study area (a collection of notably desirable neighborhoods nestled between the Minneapolis and St.\ Paul CBDs) we see a cluster of large LWR coefficients, while those areas in the southernmost portion of our region (suburban areas) have the smallest coefficients.

@@

We conducted a second series of simulation experiments aimed at testing whether the spatial variation exhibited in particular coefficients was significant or due to random chance. The mechanics of the second simulation are very similar to the those described in the previous section. We randomly changed the spatial arrangement of our house sales and re-estimated the LWR model. However, instead of examining the model fit, we compared the \emph{spread} of the regression coefficients (as measured by the standard deviation). If we observed similar levels of dispersion for variable coefficients in the randomly arranged data as in our true data, then we cannot reject the null hypothesis of a stationary relationship. However, significantly \emph{greater} dispersion of regression coefficients with our actual data would provide evidence consistent with the variable having a non-stationary relationship.

We implemented this experiment 100 times for several different bandwidths and obtained consistent results. For most variables, the standard deviation of the LWR coefficients obtained with our actual data was significantly greater than any standard deviation obtained with the randomized simulated data. We never observed a level of coefficient dispersion anywhere near the actual coefficient standard deviations for variables like house size, lot size, and most others. This can be seen in Figure~\ref{fig:MCsim2} by comparing the dashed lines of a given color to the respective solid colored distributions.\footnote{For brevity's sake we present the results for the 500 and 2,000 bandwidth sizes in Figure~\ref{fig:MCsim2}. Additional results available on request.} However, for variables like noise, owner occupancy and percent of the census block population under age 18, our observed spread in the actual LWR coefficients is similar to the simulated data. In these cases we therefore do not reject the null hypothesis of spatial stationarity. Overall, this simulation suggests that most of our variables seem to exhibit a significant non-stationary relationship with logged sales prices, but noise does not seem to be one of them.

\begin{figure}
 \makebox[\textwidth][c]{\includegraphics[height=.9\textheight]{../graphs/MCsim2FinalResults}}
 \caption{This figure shows the actual standard deviation in LWR coefficients (dashed line) compared to standard deviations obtained from 100 different instances of spatial randomization (solid lines). Results are presented for two different bandwidths (nearest 500 and 2,000 denoted by color) for each explanatory variable. In all cases the distribution of standard deviations for the smaller bandwidth is larger. In most cases the standard deviation of LWR coefficients for the actual data is substantially higher than any standard deviation obtained with the simulated data, but not for the noise variable.}
 \label{fig:MCsim2}
\end{figure}

@@

House prices fell dramatically in the United States and in our dataset during and after the Great Recession of 2008-09. We know little about the patterns of change in the hedonic price functions during and after the fall in house prices. Figures~\ref{fig:AcreTime}--\ref{fig:NoiseTime} show the spatial distribution of some our LWR hedonic coefficients for bandwidths of 500 and 2,000 nearest sales for the years 2006--2010.  The estimated LWR coefficients are different over time. In particular, the positive lot size and house size coefficients tend to decrease over time. These results are consistent with standard economic theory, as wealth and income decrease, consumer willingness to pay for normal goods decreases. What is surprising, however, is that the negative noise coefficient estimates also tend to be more negative in later years of our study. Figure~\ref{fig:NoiseTime} shows that the spatial patterns are similar across years (the most negative coefficients tend to be in the same locations across years), but the average noise coefficient tends to be more negative for the later years.

@@

Our noise variable is also a model estimate, not a direct measurement of the noise levels encountered by potential house buyers when deciding on their willingness to pay for the property. The model controls for the most important determinants of average noise exposure-- the level of the noise source, the distance and elevation change from the source, the intervening buildings, sound barriers, and foliage, but of course there is undoubtedly error. House purchasers may have visited the property on particularly busy traffic days, or on days with weather conditions more or less conducive to noise propagation across the landscape. Future researchers may seek to collect actual noise exposure data, but this will be a daunting task.

Our work faces other notable data limitations. While our house sales data were collected over the course of six years, the noise estimates are for the year 2007. To the extent that traffic flows changed with the economic recession, our noise variable could be inaccurate for other years. However, we believe these potential changes are miniscule. Table~VM2 from the US. Department of Transportation Office of Highway Policy Information website\footnote{\url{http://www.fhwa.dot.gov/policyinformation/quickfinddata/qftravel.cfm}} reports that in the year 2007 there were approximately 30 million vehicle miles traveled in the urban areas of the state of MN, while for years 2008, 2009, and 2010 the respective values were 32.5, 32.3, and 32.0 million vehicle miles. Overall, this represents a change of less than 10 percent.  Such small changes in total vehicle miles traveled will not yield significant differences in noise level estimates from our model. Given the computational complexity of re-estimating the landscape noise surface, such work is beyond the scope of this paper, but may be a worthwhile investment for future work seeking to test the robustness of our results.

@@

Monte Carlo simulation results suggest that the better goodness-of-fit provided by the local models were not due to chance and that many regression coefficients vary over space within our study area. In over a thousand different trials LWR models with spatially randomized data never fit better than global analysis and we never came close to estimating our observed house sales prices as well as we did with the local analysis on the actual data. Subsequent analysis showed that the standard deviations of most LWR coefficients with the randomized data tended to be much smaller than obtained with our actual data. While our results show very strong evidence that the coefficients on lot size and living space vary over space, the noise coefficient was one of only a few variables to not show evidence of spatial non-stationarity.

@@

Future research should be conducted in more housing markets, as the potential to apply the results of analysis in one set of geographical and economic circumstances may be limited. Second, ``mixed'' regression techniques (in which some regression coefficients are constrained to remain constant across the study area while others are allowed to vary) may allow researchers to obtain more precise estimates of the impact of hedonic characteristics by increasing the degrees of freedom in the regression. Lastly, researchers should seek to leverage improvements in spatial hedonic modelling with the advice of  \citet{Carruthers2010} and use the spatial variation in regression coefficients obtained from LWR models to estimate the second-stage hedonic regressions to identify consumer demand curves for these characteristics, thereby further improving our undertanding of the value of local amenities.

### 2014-08-18 reports/NoiseHedonicRaR.tex
contains the final version of NoiseHedonicRaR that was (re)submitted to JoRS

One way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) is through hedonic regression, examining the relationship between house prices and noise levels. \citet{Nelson1982} reviewed nine of the earliest noise hedonic articles in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel. Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities). Recent hedonic research has tended to focus on the European experience, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.

>>>>

Hedonic analysis is one way to estimate some of the costs of traffic noise (and therefore the economic benefits of policies that reduce noise) by examining the relationship between house prices and noise levels. \citet{Nelson1982} reviewed nine of the earliest hedonic studies in the United States and Canada and found an average reduction in house prices of approximately 0.4 percent per additional decibel. Many of these early studies \citep[such as][]{Gamble1974, Langley1976} are plagued by issues of small sample sizes (in the hundreds) and limited spatial extents (one or a handful of cities). Recent hedonic research has tended to focus on the European experience, often due to the availability of high quality traffic noise data made available from the government, especially the United Kingdom \citep{Day2007, Blanco2011}, Sweden \citep{Wilhelmsson2000, Andersson2010}, Switzerland \citep{Baranzini2010}, Spain \citep{MarmolejoDuarteCarlos;GonzalezTamez2009}, Netherlands \citep{Theebe2004a}, and Germany \citep{Brandt2011}.
